---
title: "Decompostion and soil C stocks "
author: "Ange-Marie BOTROH"
date: "19 mars 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Data and preanalysis

```{r message=FALSE}
source("Preanalysis_commonvariables.R")
```

##Effect of treatment 
## aleatoire variable 

##model of percent mass loss for 2 seasons
Analysis was made on 2 seasons , one season was use for exponentiel decay analysis
```{r}

#####Best model with interaction 

Best_modmixteseason2intTraitSub<- lmer(decay_rate *100 ~ Treatment + Substrate +  Gene_decomp_state + Depth_depot  + Treatment * Substrate   + (1|Sub_site) , subset(decay1and2season_vf,Growth_season == "season2")) 
#aleatoire variable site give null in vraiance so only sub_site was retain in the moddel
#Test to see on the soil layer type similar F and M subset(data,souche == 'B' | souche == 'C' ), subset(data,souche %in% c("B","C"))

anova(Best_modmixteseason2intTraitSub)
summary(Best_modmixteseason2intTraitSub)
r.squaredGLMM(Best_modmixteseason2intTraitSub) 

#Copy anavo table 
#clipcopy(round(anova(Best_modmixteseason2intTraitSub),4)) 
```


*Multiple comparaison with Emmeans 

```{r}
#### Decomposition soil layer and intercation 

#soil layer 
AMB.emm.Statdecomp_sea2_DAv <-  emmeans(Best_modmixteseason2intTraitSub, "Gene_decomp_state")

#Interaction treatment and bryopphyte groups
AMB.emm.trait_sea2int_Dav <- emmeans(Best_modmixteseason2intTraitSub,~ Treatment * Substrate , adjust = "tukey") # 

```


*Letters
```{r}
#lettre de decompstion state AMB.emm.Statdecomp_sea2_DAv

emmeansdecompstate2sea.cld <- multcomp::cld(AMB.emm.Statdecomp_sea2_DAv,  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T) #reversed permet de place les lettres dans le mem ordre que les etats
emmeansdecompstate2sea.cld


##pour modele David AMB.emm.trait_sea2int_Dav intrecartion traitement et susbstrat 

emmeanstrait_sea2int_Dav.cld <- multcomp::cld(AMB.emm.trait_sea2int_Dav,  alpha=0.05, Letters=letters,  adjust="tukey")
emmeanstrait_sea2int_Dav.cld
```


* Representation graphique 

```{r}

#decompsition and interaction bryophyte and treatement 
ggplot(emmeanstrait_sea2int_Dav.cld, aes(x=Substrate, y=emmean, color= Treatment, shape=Treatment, group=Treatment))+ geom_point(size =2.5,  position =position_dodge(0.4)) + geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, size = 1, position = position_dodge(0.4))   + theme_bw(14)  +  geom_text(aes(label = .group, y= (upper.CL + 2)),position = position_dodge(width =0.4))   +   labs( x = "Bryophytes groups", y = "Decomposition rate (%)")  + scale_shape_discrete( labels = c("Control", "CPRS", "CPRS+MSP")) + scale_color_brewer(palette = "Accent", labels = c("Control", "CPRS", "CPRS+MSP"))

#decompostion and soil layer

ggplot(emmeansdecompstate2sea.cld, aes(x=  Gene_decomp_state, y=emmean, shape = Gene_decomp_state)) + geom_point(size = 3) + scale_shape_manual(values=c(7, 14, 12,5)) + geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.05, size = 1, position = position_dodge(width = 0.3))  + theme_bw(14)  +  geom_text(aes(label = .group, y= (upper.CL + 2)),  color = "black")   +   labs( x = "Soil layer type ", y = "Decomposition rate (%)") + theme(legend.position = "none") + scale_x_discrete(labels = c("F" = "Of","M" = "Om", "H" = "Oh", "MIN" = "Min"))



```


#PCA 
##habitat factors were mesure mainly  in  season1 , analysis was made on this season  decay1and2season_vf
#Packages
```{r message=FALSE, include=FALSE}
#library(dplyr)
library(FactoMineR) #for pca
library(ade4) # for the overlay of categorical variables
library(factoextra)# for the presentation also and to calculate the contributions 
```

#PCA Analysis

```{r include=FALSE}
Mesurdata <-  filter(decay1and2season_vf, !is.na(Soil_Temp)) 
#Take for season 1
Mesurdata_saison1 <- filter(Mesurdata,Growth_season == "season1" ) 
#reaname variable
Mesurdata_saison1 <- rename(Mesurdata_saison1, "Min_to_surf_watertable_level_zone" = Thick_Water_table__minlevel_to_surf, "Peat_thickness" = Plot_peat_thickness, "Soil_temperature" = Soil_Temp, "Water_content" ="Water_content_plotmean", "C_percent" = Cpercent_plotmean,  "CN_ratio" = Ratio_CN_plotmean , "Bulk_density" = "Bulk_density_plotmean" , "Air_temperature"= Air_Temp  )

#Round up for presentation 
Mesurdata_saison1$decay_rate <- round(Mesurdata_saison1$decay_rate, 4)
#retrieve only numeric variables for the PCA
Mesurdata_Saison1_Acp <- Mesurdata_saison1[,c( c("Air_temperature", "Soil_temperature" ,  "Opening_canopy", "Water_table_level_min", "Water_table_level_max", "Water_table_level_mean" , "Peat_thickness" ))]

#Add treatment like qualtatif variable 
Mesurdata_Saison1_Acp_avecTreat <- Mesurdata_Saison1_Acp
Mesurdata_Saison1_Acp_avecTreat$Treatment <- Mesurdata_saison1$Treatment



#and if I did not take into account Air temeprature position -1, water mean poistion -6, and -9 decay rate for presentation 
Mesurdata_Saison1_Acp_avecdecay_quali <-  Mesurdata_Saison1_Acp_avecTreat[, c(-1,-6,-9)] %>% mutate ( decay_mean = ifelse(Treatment == "Control", yes = "-0.5 ± 0.945", ifelse(Treatment == "CPRS", yes = "3.347 ± 0.801","7.239 ± 0.969" )) )
 
Mesurdata_Saison1_Acp_avecdecay_quali <- Mesurdata_Saison1_Acp_avecdecay_quali %>% dplyr::select(!Treatment) 

# PCA determination
 res.pca_decayquali <- PCA(Mesurdata_Saison1_Acp_avecdecay_quali,  quali.sup = 6, graph=FALSE) # 6 is the decay column added but beacause  coord see ligne 141  this column did not use. 

#ligne 495 PCA visualisation
pvrai <- fviz_pca_biplot (res.pca_decayquali,
                col.ind = Mesurdata_Saison1_Acp_avecTreat$Treatment , palette = "Accent",
                addEllipses = TRUE, label = "var",
                col.var = "black" , repel = TRUE,
                legend.title = "Treatment") + theme_classic() +   scale_color_brewer(palette="Accent", labels = c("Control", "CPRS", "CPRS+MSP")) + scale_shape_discrete( labels = c("Control", "CPRS", "CPRS+MSP"))

##I will use this option but the values are positioned at places not too readable  
pvrai_essai <- fviz_add(pvrai, res.pca_decayquali$quali.sup$coord, color = c("#7FC97F" , "#BEAED4" , "#FDC086" ),  labelsize =4.5,geom= c("text"), repel = TRUE)
pvrai_essai

#or the one below which allows to place the decay values or we can see better according to coordinates 

# Add supplementary variables

coord <- data.frame(PC1 = c(-3.8,-1, 2.5), PC2 = c(1.5, -1.8, 1.4))
rownames(coord) <- c("-0.5 ± 0.945", "3.347 ± 0.801","7.239 ± 0.969" )  
print(coord)
pvrai <-fviz_add(pvrai, coord, color =c("#7FC97F" , "#BEAED4" , "#FDC086" ), labelsize =4.5,geom= c("text"), repel = TRUE)
pvrai 

```



#CARBON STOCKS ANALYSIS

#package see in top of code  to avoid to repeat package 
```{r echo=TRUE, message=FALSE}
#cree le 8 fevrier  2022 
library(dplyr)
library(ggplot2) #graphique
library(cowplot) # pour arranger plusieurs graphiques de ggplot  dans la mem fenetre 
library(lmerTest) #modele mixte
#library(nlme)


library(AICcmodavg) #Library for chossing the best model based AIC

#libray de stepwise
library(tidyverse)
library(caret)
library(leaps)
library(MASS)

library(MuMIn)# pour calcul de r2
library(emmeans)#pour la comparison multiple 
library(multcomp) 
#library(ggpubr)
library(rstatix) #POUR kruskal walis test

#Pour clipcopy
library("questionr") 

#pour table model
library(sjPlot)
#pour table aussi apartir de data frame 
library(formattable)

#Pour renommer les variable en naglais
library(gdata)
#recode les variables 
library(forcats)# je pouvais aussi prendre recode de mutate (recode_factor, pas très claire il marche apparement il faut etre dans lorde)
```

#Soil stocks C data ligne 65 Carbon_stock_analysis_Mars2022_VF 
```{r}
BD_Stocks_final <- read.csv2("BD_SoilCstocks.csv  ")# 

#formated data
BD_Stocks_final$Treatment <- as.factor(BD_Stocks_final$Treatment)
BD_Stocks_final$Treatment <- relevel(BD_Stocks_final$Treatment, ref = "Control")
BD_Stocks_final$Treatment <- factor(BD_Stocks_final$Treatment, levels = c("Control" ,  "CPRS",  "Harrow"))
BD_Stocks_final$Horizon_name <- as.factor(BD_Stocks_final$Horizon_name)
BD_Stocks_final$Horizon_name <- factor(BD_Stocks_final$Horizon_name, levels = c("F" ,  "M",  "H" ,  "Min"))
BD_Stocks_final$plant_group <- as.factor(BD_Stocks_final$plant_group) #Not use

str(BD_Stocks_final) 
BD_Stocks_final$Thickness_refcontrolmodif <- scale(BD_Stocks_final$Thickness_refcontrolmodif)
```

###Models For total carbon stokcs ( organic and min) 

```{r}
#
modstocks_Total<- lmer(log(C_Quantity_totalprofiltha) ~ Treatment *Thickness_refcontrolmodif  + (1|Sub_site) ,distinct(BD_Stocks_final, C_Quantity_totalprofiltha, .keep_all = T)) #  (1|Site) lead  a singularity error 
#For total stocks it is important  to put distinct on data to take ony 45 points because values were repeated
summary(modstocks_Total)
anova(modstocks_Total)

#Emmeans de prtofil entienr orga jusuqau sol mineal 
emmeans_stocktotalprofil_response_withLetter <- multcomp::cld(emmeans(modstocks_Total,"Treatment" , transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
emmeans_stocktotalprofil_response_withLetter

#Total Organic profil 

modstocks_TotalOrga<- lmer(log(C_Quantity_totalprofil_Orga_tha) ~ Treatment *  Thickness_refcontrolmodif + (1|Sub_site) , distinct(BD_Stocks_final, C_Quantity_totalprofil_Orga_tha, .keep_all = T)) 
summary(modstocks_TotalOrga)
 anova(modstocks_TotalOrga)
 emmeans_stocktotalOrga_response_withLetter <- multcomp::cld(emmeans(modstocks_TotalOrga,"Treatment" , transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
 emmeans_stocktotalOrga_response_withLetter
# 
# #clipcopy(round(anova(modstocks_TotalOrga),4))
```

#stocks evoultion according thickness 

```{r}
boot_res <- bootMer(modstocks_TotalOrga, function(x) predict(x, re.form = NA), nsim = 200)

 

BD_Stocks_final_forboot <- mutate(distinct(BD_Stocks_final, C_Quantity_totalprofil_Orga_tha, .keep_all = T),

                               pred = predict(modstocks_TotalOrga, re.form = NA),

                               lo = apply(boot_res$t, 2, quantile, probs = 0.025),

                               hi = apply(boot_res$t, 2, quantile, probs = 0.975))

 
ggplot(BD_Stocks_final_forboot, aes(x = Thickness_refcontrolmodif, y = log(C_Quantity_totalprofil_Orga_tha), fill = Treatment, color = Treatment)) +

    geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.3) +

    geom_line(aes(y = pred)) +

    geom_point(aes(color = Treatment)) + 
  scale_color_brewer(palette = "Accent") + scale_fill_brewer(palette = "Accent", labels = c("Control", "CPRS", "CPRS+MSP"))  + scale_color_brewer(palette = "Accent", labels = c("Control", "CPRS", "CPRS+MSP"))  + 
  theme_classic(14) + labs( x = "Organic layer thickness before treatment (cm)", y = "log(Organic soil carbon stocks (t/ha))")
```


#for variable others
##For all details variables used to calcuate Carbon stocks 
#For C_percent 
```{r}
#Global not by horizon
modCpercent_general<- lmer(C_percent ~  Treatment    + (1|Site)   ,BD_Stocks_final)  #Thickness_ref
summary(modCpercent_general)
anova(modCpercent_general)
multcomp::cld(emmeans(modCpercent_general, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)

#HorizonF
modCpercent_F<- lmer(C_percent ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="F")) 
summary(modCpercent_F)
anova(modCpercent_F)
#emmeans(modCpercent_F, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modCpercent_F, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
 
 #Horizon M
modCpercent_M<- lmer(C_percent ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="M")) #+ Thickness_ref
summary(modCpercent_M)
anova(modCpercent_M)
multcomp::cld(emmeans(modCpercent_M, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T) #

#Horizon H
modCpercent_H<- lmer(C_percent ~  Treatment   + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="H")) #
summary(modCpercent_H)
anova(modCpercent_H)
multcomp::cld(emmeans(modCpercent_H, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T) #


#Horizon Min
modCpercent_Min<- lmer(C_percent ~  Treatment  + (1|Site) ,subset(BD_Stocks_final,  Horizon_name =="Min"))
summary(modCpercent_Min)
anova(modCpercent_Min)
multcomp::cld(emmeans(modCpercent_Min, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
```

#For Bulk density 
```{r}
#Global not by horizon
modBulkdens_general<- lmer(log(Bulk_density)  ~  Treatment  + (1|Site)   ,BD_Stocks_final) 
summary(modBulkdens_general)

anova(modBulkdens_general)
#emmeans(modBulkdens_general, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modBulkdens_general, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)

#HorizonF
modBulkdens_F<- lmer(log(Bulk_density) ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="F")) 
summary(modBulkdens_F)

anova(modBulkdens_F)
#emmeans(modBulkdens_F, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modBulkdens_F, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
 
#Horizon M
modBulkdens_M<- lmer(log(Bulk_density) ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="M")) 
summary(modBulkdens_M)

anova(modBulkdens_M)
#emmeans(modBulkdens_M, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modBulkdens_M, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)

#Horizon H
modBulkdens_H<- lmer(log(Bulk_density) ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="H")) 
summary(modBulkdens_H)

anova(modBulkdens_H)
multcomp::cld(emmeans(modBulkdens_H, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T) #


#Horizon Min
modBulkdens_Min<- lmer(log(Bulk_density) ~  Treatment  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="Min")) 
summary(modBulkdens_Min)
anova(modBulkdens_Min)
multcomp::cld(emmeans(modBulkdens_Min, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
```

#For thickness 
```{r}
#HorizonF
modThickHori_F<- lmer(log(Total_thickness_horizon) ~  Treatment +Thickness_refcontrolmodif  + (1|Sub_site)   ,subset(BD_Stocks_final,  Horizon_name =="F")) #ICI mettre aussi les sub_site car les site svcre une erreur de singularité et na,rrive pas trouver de différence entre le emmeans alrs que anova dit qu'il ya un effet des traitements
summary(modThickHori_F)
anova(modThickHori_F)
#emmeans(modThickHori_F, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modThickHori_F, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
 
#Horizon M
modThickHori_M<- lmer(log(Total_thickness_horizon) ~  Treatment * Thickness_refcontrolmodif  + (1|Site)+  (1|Sub_site)   ,subset(BD_Stocks_final,  Horizon_name =="M")) #(1|Site)
summary(modThickHori_M)
anova(modThickHori_M)
#emmeans(modThickHori_M, "Treatment", transform = "log", type = "response")
multcomp::cld(emmeans(modThickHori_M, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)

#Horizon H
modThickHori_H<- lmer(log(Total_thickness_horizon) ~  Treatment * Thickness_refcontrolmodif  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="H"))
summary(modThickHori_H)
anova(modThickHori_H)
multcomp::cld(emmeans(modThickHori_H, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T) #


#Horizon Min
modThickHori_Min<- lmer(log(Total_thickness_horizon) ~  Treatment * Thickness_refcontrolmodif  + (1|Site)   ,subset(BD_Stocks_final,  Horizon_name =="Min"))
summary(modThickHori_Min)
anova(modThickHori_Min)
multcomp::cld(emmeans(modThickHori_Min, "Treatment", transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
```

* For total thickness 

```{r}
#Total profil
modThicktotal<- lmer(log(Total_thickness_OrgaMin)~ Treatment  *  Thickness_refcontrolmodif   + (1|Site) + (1|Sub_site),BD_Stocks_final)
summary(modThicktotal)
anova(modThicktotal) #
pairs(emmeans(modThicktotal, "Treatment"))
multcomp::cld(emmeans(modThicktotal,"Treatment" , transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)

#Organic
modThickOrga<- lmer(log(Total_thickness_Organic )~ Treatment  *   Thickness_refcontrolmodif   + (1|Site) + (1|Sub_site),BD_Stocks_final)
summary(modThickOrga)
anova(modThickOrga) #
#pairs(emmeans(modThickOrga, "Treatment")) 
multcomp::cld(emmeans(modThickOrga,"Treatment" , transform = "log", type = "response"),  alpha=0.05, Letters=letters,  adjust="tukey", reversed = T)
```



#puissance of analisys see code ligne 201
##On total stocks puissance
```{r}
#Take values in summary(modstocks_Total)
#SE std.error
SE_profiltot_Harrow <- 1.277716 
SE_profiltot_CPRS <-  1.221207


#df =degre de liberte 

df_profiltot_Harrow <- 34.981840
df_profiltot_CPRS <- 34.227270 


#Calcul de n et SD

n_profiltot_Harrow <- df_profiltot_Harrow + 1 
n_profiltot_CPRS = df_profiltot_CPRS +1 

SD_profiltot_Harrow <- SE_profiltot_Harrow * sqrt(n_profiltot_Harrow)
SD_profiltot_CPRS <-  SE_profiltot_CPRS * sqrt(n_profiltot_CPRS)


##Calculation of the delta (difference between means) to have a power of 80%
pwt_harrow <- power.t.test(n = n_profiltot_Harrow, power = 0.8, sd = SD_profiltot_Harrow, type = "one.sample") ; pwt_harrow
pwt_CPRS <- power.t.test(n = n_profiltot_CPRS, power = 0.8, sd = SD_profiltot_CPRS, type = "one.sample"); pwt_CPRS

#See delta in the C stocks mesure scale  
delta_har <- exp( pwt_harrow$delta) ; delta_har
delta_Cprs <- exp(pwt_CPRS$delta) ; delta_Cprs
```



